### 2021-04-10 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsection{Attack Models}
Previous work~\cite{182946} classifies the address-based side-channel attacks into three type based on the type of information that an attacker can learn during the attack.
\subsubsection*{Time-based Attacks}
In time-based attacks, an attacker can monitor the execution time of a victim. It could be the overall execution time or the execution time of some interesting points (e.g. a function).  The execution time is correlated to some events (e.g., cache hits, cache misses, page faults) during the execution. Example of those attacks include remote timing attacks, Bernstein attack on AES, and Kocher’s original attack from CRYPTO 96.
\subsubsection*{Access-based Attacks}
\subsubsection*{Trace-based Attacks}

>>>>

\subsection{Attack Models}
Previous work~\cite{182946} classifies the address-based side-channel attacks into three type based on the type of information that an attacker can learn during the attack.
\subsubsection*{Time-based Attacks}
In time-based attacks, an adversary can monitor the execution time of a victim. It could be the overall execution time or the execution time of some interesting points (e.g. a function).  The execution time is correlated to some events (e.g., cache hits, cache misses, page faults) during the execution. Example of those attacks include remote timing attacks, Bernstein attack on AES, and Kocher’s original attack from CRYPTO 96.
\subsubsection*{Access-based Attacks}
In access-based attacks, an adversary can 
\subsubsection*{Trace-based Attacks}
